
%!TEX TS-program = xelatex
\documentclass[letterpaper,10pt]{article}

%A Few Useful Packages
\usepackage{marvosym}
\usepackage{fontspec} 					%for loading fonts
\usepackage{xunicode,xltxtra,url,parskip} 	%other packages for formatting
\RequirePackage{color,graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[
  margin=1in,
  includefoot,
  footskip=30pt, 
  headheight=2cm, 
  headsep=24pt
]{geometry}
\usepackage{layout}
\usepackage{supertabular} 				%for Grades
\usepackage{titlesec}					%custom \section
\usepackage{multirow}
\usepackage{etaremune}
\usepackage{pdfpages}
\usepackage{fancyhdr}
\usepackage{longtable}
\usepackage{setspace}
\usepackage{color,soul}
\renewcommand{\headrulewidth}{0pt}
\usepackage{wrapfig}
\usepackage{lastpage}
\usepackage{amsmath}
\usepackage{enumitem}
\usepackage{pdfpages} %for including publications 
\usepackage{graphicx} %for siganture
\pagestyle{fancyplain}
\fancyhf{}

\lfoot{\fancyplain{}{\small Gordon J. Getzinger}}
\cfoot{\fancyplain{}{\small \today}}

%Setup hyperref package, and colours for links
\usepackage{hyperref}
\definecolor{linkcolour}{rgb}{0,0,0}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}

%FONTS
\defaultfontfeatures{Mapping=tex-text}
\renewcommand{\familydefault}{\sfdefault}

\newcommand{\etal}{\textit{et al}. }
\newcommand{\ie}{\textit{i}.\textit{e}., }
\newcommand{\eg}{\textit{e}.\textit{g}. }

%\titleformat{\section}{\large\scshape\raggedright}{}{0em}{}[\titlerule]
\titleformat{\section}{\large\rmfamily\scshape\raggedright}{}{0em}{}[\titlerule]

\titlespacing{\section}{0pt}{3pt}{3pt}

\titlespacing\subsection{0pt}{3pt}{0pt}
\titlespacing\subsubsection{0pt}{3pt}{0pt}

\titleformat*{\subsection}{\normalsize\bfseries}
\titleformat*{\subsubsection}{\normalsize\bfseries}
\titleformat*{\paragraph}{\large\bfseries}
\titleformat*{\subparagraph}{\large\bfseries}
\hyphenation{im-pre-se}

%-------------WATERMARK TEST [**not part of a CV**]---------------
\usepackage[absolute]{textpos}

\setlength{\TPHorizModule}{30mm}
\setlength{\TPVertModule}{\TPHorizModule}
\textblockorigin{2mm}{0.65\paperheight}
\setlength{\parindent}{0pt}


%---------------LABELING LIST STRUCTURE 

%--------------------BEGIN DOCUMENT----------------------
\begin{document}
%\include{ncsu_2019_CoverLetter}
\setlength{\voffset}{0in}
\rhead{}
\lhead{}
%\tableofcontents
\lfoot{\fancyplain{}{\footnotesize Gordon J. Getzinger}}
\cfoot{\fancyplain{}{\footnotesize Page \thepage \hspace{1pt} of \pageref{LastPage}}}

\newgeometry{margin=1in,
  includefoot,
  footskip=30pt} 
\singlespacing
\setlength{\parindent}{0pt}
%\fontsize{10}{12}\selectfont
%--------------------TITLE-------------
\par{\centering
		{\Large\rmfamily\scshape Gordon J. Getzinger, PhD}\\[0.5em]
		%{\small Falk Foundation Environmental Exposomics Laboratory \\ Duke University} \\[0.5em]
		{\footnotesize 
			%\href{https://falk.exposomics.duke.edu/people/gordon-getzinger}{falk.exposomics.duke.edu} \\
			%\href{https://scholars.duke.edu/person/gordon.getzinger}{https://scholars.duke.edu/person/gordon.getzinger}\\
			%\href{https://www.exponent.com/professionals/g/getzinger-gordon}{\textcolor{blue}{exponent.com/professionals/g/getzinger-gordon}}\\
			\href{https://orcid.org/0000-0002-5628-1425}{\textcolor{blue}{ORCID 0000-0002-5628-1425}}\\
			%\href{https://scholar.google.com/citations?user=kASr4hEAAAAJ&hl=en}{\textcolor{blue}{scholar.google.com/citations?user=kASr4hEAAAAJ\&hl=en}}\\
			%\href{https://github.com/gjgetzinger}{\textcolor{blue}{github.com/gjgetzinger}} \\\\
			73 Martin St. Apt 45, Cambridge, MA \\
			(330) 593-9622 \\
			\href{mailto:ggetzinger@exponent.com}{ggetzinger@exponent.com}
		}
		\par}
%--------------------SECTIONS-----------------------------------
\rfoot{\footnotesize Curriculum vitae} 
%%%%%%%%%%%%%%%
%Section: Appointments
\section{Experience}
\begin{itemize}
\item {\bfseries Scientist}, Environmental and Earth Sciences, Exponent, Inc. (2020-present)
\item {\bfseries Research Scientist}, Department of Civil and Environmental Engineering and Nicholas School of the Environment, Duke University (2019-2020)
%\item {\bfseries Cheminformatics Scientist}, North Carolina Per- and Polyfluoroalkyl Substance Testing Network (2019-2020)
%\item {\bfseries Director}, Development Core, Duke Environmental Analysis Laboratory, Human Health Exposure Analysis Resource (2019-2020)
\end{itemize}
%\section{Relevant Experience} 
%\begin{itemize} 
%\item As an Environmental Chemist I have worked broadly to provide analytical measurements to inform risk assessment of organic pollutants in diverse environmental media. 
%\item In the preparation of scientific reports and data products, I have synthesized scientific literature on contaminant risk in order to provide context for measured pollutants.  
%\end{itemize} 
%%%%%%%%%%%%%%%
%Section: Education
\section{Education and Training}
\begin{itemize}
	\item {\bfseries Postdoctoral Associate}, Department of Environmental Systems Science, Institute of Biogeochemistry and Pollutant Dynamics, ETH Zurich (2016 - 2019)
	\item {\bfseries PhD}, Nicholas School of the Environment, Duke University (2010-2016)
	\item {\bfseries BA} in Chemistry and {\bfseries BS} in Environmental Science, Loyola University Chicago (2006-2010)
\end{itemize}
\begin{center}
%%%%%%%%%%%%%%%
%Section: Awards and Honors
\section{Awards \& Honors}
\begin{itemize}
\item U.S. National Science Foundation, Honorable Mention, Graduate Research Fellowship, May 2010.
\item Department of Chemistry, Loyola University Chicago, Sarussi Scholarship for Undergraduate Research in Organic Synthesis, May 2007. 
\item Loyola University Chicago, Jesuit High School Presidential Scholarship, 2006-2010. 
\end{itemize}
\end{center}
%
%\section{Research Support: Current} 
%\begin{itemize}
%\item Improving Interoperability and Reuse of Chemical Information in Superfund Research Projects; PI; National Institute of Environmental Health Sciences; \$261,070.00; 7/1/2019-3/31/2020. 
%\item Duke Environmental Analysis Laboratory (PI-Stapleton); Development Core Director; National Institute of Environmental Health Sciences; \$5,000,000.00; 9/10/2019-5/3/2024. 
%\end{itemize} 
%
%\section{Research Support: Pending} 
%\begin{itemize}
%\item Assessment of Contaminant Mobilization and Risk to Vulnerable Populations in Easter North Carolina After Extreme Storm Events; co-PI; US Environmental Protection Agency. 
%\end{itemize}
%
%Section: Publications in Refereed Journals
\section{Peer-Reviewed Journal Publications}
\begin{etaremune}
%
\item {\bfseries Getzinger, G.J.}; Higgins, C.P.; Ferguson, P.L.;  Structure Database and In Silico Spectral Library for Comprehensive Suspect Screening of Per- and Polyfluoroalkyl Substances (PFASs) in Environmental Media by High-resolution Mass Spectrometry, \emph{Analytical Chemistry} {\bfseries 2021}, \href{https://doi.org/10.1021/acs.analchem.0c04109}{\textcolor{blue}{10.1021/acs.analchem.0c04109}}
%
\item {\bfseries Getzinger, G.J.}; Ferguson, P.L.;  Illuminating the exposome with high-resolution accurate-mass mass spectrometry and nontargeted analysis, \emph{Current Opinion in Environmental Science \& Health} {\bfseries 2020}, \href{https://doi.org/10.1016/j.coesh.2020.05.005}{\textcolor{blue}{10.1016/j.coesh.2020.05.005}}
% 
\item Manfrin, A.; Nizkorodov, S.; Malecha, K.; {\bfseries Getzinger, G.J.}; McNeill, K.; Borduas-Dedekind, N. Reactive Oxygen Species Production From Secondary Organic Aerosols: The Importance of Singlet Oxygen.  \emph{Environ. Sci. Technol.} {\bfseries 2019}, \href{https://doi.org/10.1021/acs.est.9b01609}{\textcolor{blue}{10.1021/acs.est.9b01609}}
%
\item Evans, M.;  {\bfseries Getzinger, G. J.} ; Luek, J.; Hanson, A.; McLaughlin, M.; Blotevogel, J.; Welch, S.; Nicora, C.; Purvine, S.; Xu, C.; Cole, D.; Darrah, T.; Hoyt ,D.; Metz, T.; Ferguson, P.L.; Lipton, M.; Wilkins, M.; Mouser, P. In situ transformation of ethoxylate and glycol surfactants by shale-colonizing microorganisms during hydraulic fracturing. \emph{The ISME Journal} {\bfseries 2019}, \href{https://doi.org/10.1038/s41396-019-0466-0}{\textcolor{blue}{10.1038/s41396-019-0466-0}}
%
\item De Hoe,G; Zumstein, Z; {\bfseries Getzinger, G.J.}, Ruegsegger, I; Kohler, H.E.; Maurer-Jones, M.A.; Sander, M; Hillmyer, M.A.; McNeill, K.. Photochemical Transformation of Poly(butylene adipate-co-terephthalate) and Its Effects on Enzymatic Hydrolyzability. \emph{Environ. Sci. Technol.} {\bfseries 2019}, \href{http://dx.doi.org/10.1021/acs.est.8b06458}{\textcolor{blue}{10.1021/acs.est.8b06458}}
%
\item Walpen, N.; Lau, M.; Fiskal, A.; {\bfseries Getzinger, G. J.}; Meyer, S; Nelson, T; Lever, M; Schroth, M.H.; Sander, M, Oxidation of Reduced Peat Particulate Organic Matter by Dissolved Oxygen: Quantification of Apparent Rate Constants in the Field. \emph{Environ. Sci. Technol.} {\bfseries 2018}, 52(19) \href{http://dx.doi.org/10.1021/acs.est.8b03419}{\textcolor{blue}{10.1021/acs.est.8b03419}}
%
\item Walpen, N.; {\bfseries Getzinger, G. J.}; Schroth, M.H.; Sander, M, Electron-donating Phenolic and Electron-accepting Quinone Moieties in Peat Dissolved Organic Matter: Quantities and Redox Transformations in the Context of Peat Biogeochemistry. \emph{Environ. Sci. Technol.} {\bfseries 2018}, 52 (9). \href{http://dx.doi.org/10.1021/acs.est.8b00594}{\textcolor{blue}{10.1021/acs.est.8b00594}}
%
\item Hoelzer, K.; Sumner, A. J.; Karatum, O.; Nelson, R. K.; Drollette, B. D.; O'Connor, M. P.; D'Ambro, E. L.; {\bfseries Getzinger, G. J.}; Ferguson, P. L.; Reddy, C. M.; Elsner, M.; Plata, D. L., Indications of Transformation Products from Hydraulic Fracturing Additives in Shale-Gas Wastewater. \emph{Environ. Sci. Technol.} {\bfseries 2016}, 50 (15).\href{http://dx.doi.org/10.1021/acs.est.6b00430}{\textcolor{blue}{10.1021/acs.est.6b00430}}
%
\item Li, H; { \bfseries Getzinger, G. J.}; Ferguson, P.L.; Orihuela, B; Zhu, Mei; Rittschof, D. Effects of Toxic Leachates from Commercial Plastics on Larval Survival 
  and Settlement of the Barnacle Amphibalanus amphitrite. \emph{Environ. Sci. Technol.} {\bfseries 2015}, 50 (2). \href{http://dx.doi.org/10.1021/acs.est.5b02781}{\textcolor{blue}{10.1021/acs.est.5b02781}}
  %
\item { \bfseries Getzinger, G. J.}; O'Connor, M.P.; Hoelzer, K.; Drollette, B.D.; Karatum, O.; Deshusses, M.A.; Ferguson, P.L.; Elsner, M.; Plata, D.L. Natural Gas Residual Fluids: Sources, Endpoints, and Organic Chemical Composition after Centralized Waste Treatment in Pennsylvania. \emph{Environ. Sci. Technol.} {\bfseries 2015}, 51 (60). \href{http://dx.doi.org/10.1021/acs.est.5b00471}{\textcolor{blue}{10.1021/acs.est.5b00471}}
%
\item Fang, M.; { \bfseries Getzinger, G. J.}$^*$; Cooper, E. M.; Clark, B. W.; Garner, L. V. T.; Giulio, R. T. D.; Ferguson, P. L.; Stapleton, H. M., Effect-directed analysis of Elizabeth river pore water: Developmental toxicity in zebrafish (Danio rerio). \emph{Environ Toxicol Chem} {\bfseries 2014}, 30. \href{http://dx.doi.org/10.1002/etc.2738}{\textcolor{blue}{ 10.1002/etc.2738}} \\ $^*$ co-first author. 
%
\item Stapleton, H.M.; Sharma, S.; {\bfseries Getzinger, G. J.}; Ferguson, P.L.; Gabriel, T.; Webster, F.; Blum, A. Novel and High Volume Flame Retardants in US Couches Reflective of the 2005 PentaBDE Phase Out. \emph{Environ. Sci. Technol.} {\bfseries 2012}, 46 (24). \href{http://dx.doi.org/10.1021/es303471d}{\textcolor{blue}{10.1021/es303471d}}.
\end{etaremune}
%
%MANUSCRIPTS IN REVISION
\section{Manuscripts in Revision}
\begin{etaremune}
\item {\bfseries Getzinger, G.J.}; Ferguson, P.L.;  High-throughput Trace-level Suspect Screening for Per- and Polyfluoroalkyl Substances in Environmental Waters by Peak-focusing Online Solid Phase Extraction and High-resolution Mass Spectrometry, \emph{ES\&T Water} 
\end{etaremune}
%
% SUBMITTED MANUSCRIPTS 
%\section{Manuscripts in Review}
%\begin{etaremune}
%\end{etaremune}
%
%Invited Speaker at Universities and Institutions
\section{Invited Speaker at Universities and Institutions} 
\begin{etaremune}
\item{{\bfseries Getzinger, G.J.}} Non-target analysis of organic pollutants: A platform for data-driven assessment of aquatic environments. University of Cincinnati. July 2018.
\item{{\bfseries Getzinger, G.J.}} Non-target analysis of organic pollutants: A platform for data-driven assessment of aquatic environments. Big Data in Environmental Sciences Workshop, ETH Zurich. April 2018.
\item{{\bfseries Getzinger, G.J.}} Non-target analysis: Enabling data driven environmental sciences. Swiss Federal Institute of Aquatic Science and Technology (Eawag). November 2017.
\item{{\bfseries Getzinger, G.J.}}; Ferguson, P.L. Exploring environmentally relevant chemical space through ultrahigh resolution mass spectrometry, computational mass spectrometry and chemoinformatics: The example of wastewater derived organic micropollutants. National Center for Computational Toxicology, U.S.  EPA. Research Triangle Park, NC. May 2016.
% 
\item {\bfseries Getzinger, G.J.}; Ferguson, P.L., Non-targeted identification of wastewater and stormwater derived organic micropollutants in the Ellerbe Creek Watershed (Durham, NC) by HPLC-high resolution mass spectrometry. Triangle Area Mass Spectrometry Discussion Group. Research Triangle Park, NC. May 2013. 
%
\item {\bfseries Getzinger, G.J.}; Ferguson, P.L. Non-targeted analysis of emerging contaminants in wastewater impacted aquatic environments. Thermo Scientific User's Meeting at the Annual Meeting of the American Society for Mass Spectrometry. Vancouver, BC. May 2012.
\end{etaremune}
%
%Conference proceedings
\section{Conference Talks as Presenter}
\begin{etaremune}
	\item{{\bfseries Getzinger, G.J.}}; Ferguson, P.L.  Improving non-target identification of organic contaminants: Probabilistic ranking of structure assignments by computational mass spectrometry. National Meeting of the American Chemical Society. Orlando, FL. April 2019.
	\item{{\bfseries Getzinger, G.J.}}; Ferguson, P.L. Exploring environmentally relevant chemical space through ultrahigh resolution mass spectrometry, computational mass spectrometry and chemoinformatics: The example of wastewater derived organic micropollutants. Congressi Stefano Franscini on Non-target screening of organic chemicals for a comprehensive environmental risk assessment. Ascona, Switzerland. May 2016. 
	\item{{\bfseries Getzinger, G.J.}}; Ferguson, P.L. Aryl Phosphite Antioxidants as Molecular Markers of Plastic Particles in Marine Environments. National Meeting of the Society of Environmental Toxicology and Chemistry. Salt Lake City, UT. November 2015.
	\item{{\bfseries Getzinger, G.J.}}; Ferguson, P.L. Identifying transformation products of organic micropollutants in conventional wastewater treatment by high-resolution mass spectrometry and differential non-targeted screening. National Meeting of the American Chemical Society. Boston, MA. August 2015.
	\item {\bfseries Getzinger, G.J.}; Ferguson, P.L. Non-targeted analysis of emerging contaminants in wastewater and wastewater impacted aquatic environments. Society of Environmental Toxicology and Chemistry. Long Beach, CA.  November 2012. 
\end{etaremune}
%
%Webinars
\section{Webinars}
\begin{etaremune}
\item {\bfseries Getzinger, G.J.}; Beck, J. Analysis of Targeted and Non-targeted Contaminants in Storm Water Retention Ponds. Chemical and Engineering News Webinar. July 2013.
\end{etaremune}
%
%Conference Poster Presentations 
\section{Conference Poster Presentations}
\begin{etaremune}
\item{}{\bfseries Getzinger, G.J.}; Sander, M. On the molecular composition of phenolic dissolved organic matter in bogs. Gordon Research Conference, Environmental Sciences: Water, Holderness, NH. June 2018. 
%
\item{{\bfseries Getzinger, G.J.}}; Ferguson, P.L. Exploring environmentally relevant chemical space: The example of wastewater derived organic micropollutants. Gordon Research Conference, Environmental Sciences: Water. Holderness, NH. June 2016.
%
\item{\bfseries Getzinger, G.J.}; Ferguson, P.L.. Occurrence and Fate of Aryl Phosphite Polymer Additives in Marine Sediments. Annual meeting of the Association of Environmental Engineering and Science Professors. New Haven, CT. June 2015.
%
\item {\bfseries Getzinger, G.J.}; Ferguson, P.L.; McNeill, K. Photosensitized Transformations of Aryl Phosphite Polymer Additives. Gordon Research Conference, Environmental Sciences: Water. Holderness, NH.  June 2014.
%
\item {\bfseries Getzinger, G.J.}; Ferguson, P.L.; Beck, J.; Yang, C.; Schoutsen, F. Analysis of Targeted and Non-Targeted Identified Contaminants in Storm Water Retention Ponds Using LC-HRMS With Online Solid Phase Extraction. Annual Meeting of the American Society of Mass Spectrometry. Minneapolis, MN. June 2013.
%
\item  {\bfseries Getzinger, G.J.}; Ferguson, P.L. Non-targeted analysis of emerging contaminants in wastewater impacted environments. Gordon Research Conference, Environmental Sciences: Water. Holderness, NH.  June 2012.
%
 \item  {\bfseries Getzinger, G.J.}; Ferguson, P.L. Two-dimensional liquid chromatography high resolution mass spectrometry for the analysis of polar organic contaminants in the aquatic environment. Society of Environmental Toxicology and Chemistry Annual Meeting, Boston, MA. November 2011.
%
 \item {\bfseries Getzinger, G.J.}; Ferguson, P.L. Two-dimensional liquid chromatography high resolution mass spectrometry for the analysis of complex environmental samples. International Conference of Chemistry and the Environment, Zurich Switzerland. September 2011.
%
 \item {\bfseries Getzinger, G.J.}; Ferguson P.L. Analysis of oil spill dispersants and degradation products in seawater by two-dimensional liquid chromatography-high resolution mass spectrometry. Society of Environmental Toxicology and Chemistry Gulf Oil Spill Meeting, Pensacola Beach, FL. April 2011.
%
 \item {\bfseries Getzinger, G.J.}; Ferguson, P.L. Analysis of oil spill dispersants and degradation products in seawater by liquid-chromatograph-high resolution Orbitrap mass spectrometry. Society of Environmental Toxicology and Chemistry Annual Meeting, Portland, OR. November, 2010.
\end{etaremune}
%
%%%%%%%%%%%%%%%
%TEACHING EXPERIENCE 
\section{Teaching Experience}
\begin{itemize}
	\item {\bfseries Course Developer and Instructor} for Environmental Photochemistry Practicum, \emph{Institute of Biogeochemistry and Pollutant Dynamics, Department of Environmental Systems Science, ETH Zurich} (Spring 2018)
	\item {\bfseries Course Manager and Teaching Assistant Supervisor} for Introductory Chemistry Practicum, \emph{Institute of Biogeochemistry and Pollutant Dynamics, Department of Environmental Systems Science, ETH Zurich} (Winter 2018)
	\item {\bfseries Guest Instructor} for Introduction to Environmental Organic Chemistry, \emph{Institute of Biogeochemistry and Pollutant Dynamics, Department of Environmental Systems Science, ETH Zurich} (Fall 2016-17)
	\item  {\bfseries Guest Instructor} for Environmental Analytical Chemistry , \emph{Department of Civil and Environmental Engineering, Duke University} (Fall \& Spring 2012)
	\item {\bfseries Teaching Assistant} for Environmental Chemistry and Toxicology, \emph{Nicholas School of the Environment, Duke University} (Spring 2011)
	\item {\bfseries Teaching Assistant} for Environmental Aquatic Chemistry, \emph{Department of Civil and Environmental Engineering, Duke University} (Fall 2010)
	\item {\bfseries Teaching Assistant} for Introductory Organic Chemistry Laboratory, \emph{Department of Chemistry, Loyola University Chicago} (2008-2010)
\end{itemize}
%
%Section: Honors and Awards
%Editorial Contributions
%Media Coverage 
%
%%%%%%%%%%%%%
%RESEARCH ADVISEES
\section{Research Advisees } 
%\subsection*{Bachelor Thesis Supervised}
\begin{etaremune}
\item Reto Gubler, \emph{Bachelor Thesis}, ''Quantifying Electrophilic Moieties in Dissolved Organic Matter with Biologically Relevant Nucleophiles'', ETH Zurich, Summer 2017.
\item Oskar J\"{o}nsson, \emph{Bachelor Thesis}, ''Steady-state Concentrations of Photochemically Produced Reactive Intermediates in Peatland Pool and Pore Waters: Implications for Carbon Export from Northern Peatlands'', ETH Zurich, Fall 2016.
\end{etaremune}
%
%%%%%%%%%%%%%%%%
%Graduate Thesis Committees 
%%%%%%%%%%%%%
%Professional Affiliations 
\section{Professional Affiliations and Service} 
\begin{itemize}
%Conferences organized 
\item \textbf{Conferences Organized:} 
\begin{itemize}
\item \emph{Organizing Committee}, Non-target Analysis for Comprehensive Environmental Assessment, SETAC Focus Topic Meeting (2020).
\item \emph{Chair}, Gordon Research Seminar on Environmental Sciences: Water (2016).
\end{itemize}
%Conference symposia chaired
\item \textbf{Conference Symposia Chaired:} 
\begin{itemize}
\item {} \emph{Discussion Leader}, Gordon Research Seminar on Environmental Sciences: Water (2014)
\item {} \emph{Session Co-chair}, \emph{''Helping Contaminants Emerge: Non-targeted and Effect-directed Environmental Analysis''}, National meeting of the Society of Environmental Toxicology and Chemistry (2014)
\end{itemize}
\item \textbf{Memberships:} American Chemical Society, Division of Environmental Chemistry; Society of Environmental Toxicology and Chemistry.
\item \textbf{Peer-reviewer:} Chemosphere,  Environment International, Environmental Science and Technology, Environmental Science and Technology Letters, Environmental Sciences: Processes and Impacts, Journal of the American Society for Mass Spectrometry, Science Advances,Water Research.
\end{itemize}
%
%\section{Submitted or in preparation manuscripts} 
%\begin{enumerate} 
%\item {\bfseries Getzinger, G.J.}; Walpen, N.; Sander, M., On the Molecular Composition of Phenolic Dissolved Organic Matter in Bogs. \emph{in prep}
%\item {\bfseries Getzinger, G.J.}; Sander, M., Molecular Weight Distribution of Redox-active Moieties in Organic Matter Isolates. \emph{in prep} 
%\item {\bfseries Getzinger, G.J.}; Ferguson, P.L., An Empirical Model for Scoring Structural Annotations of Organic Pollutants by High-resolution Mass Spectrometry. \emph{in prep}
%\item {\bfseries Getzinger, G.J.}; Ferguson, P.L.; Muir, D., A Structure Oriented Classification of Environmentally Relevant Chemical Space. \emph{in prep} 
%\item Evans, M.; {\bfseries Getzinger, G.J.}; Blotevogel, J.; Borton, M.; Welch, S.; Hoyt, D.; Plata, D.; Ferguson, P.L.; Cole, D.; Wilkins, M.; Wrighton, K.; Mouser, P.J., In Situ Degradation of Hydraulic Fracturing Surfactants by Produced Fluid Microorganisms. \emph{in prep}
%\end{enumerate}

\end{document}

%Technical Advisory 
%Service and Outreach Activities  
%Current Grants 
%Past Grants
%Invited Speaker at Conferences  
%\pagebreak